Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-03-31 GWLDCII.tex
some use of the GN function notation

Now consider $I_{n-2}^{W}$. If $n-2\not\in I_{n-2}^{V}$ (i.e. $n-2$ supports no propagators in $V$), then in $W$ the algorithm assigns $p$ to $n-2$ and this does not affect the rest of the construction of $I_{n-2}^{V}$, so we obtain $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-2\}$ as above.

On the other hand, if $n-2\in I_{n-2}^{V}$ then we must be in the right hand case of Figure~\ref{fig special p} and the algorithm assigns $q$ to vertex $n-2$ in both $V$ and $W$ (since $q$ is always the clockwise-most propagator supported on vertex $n-2$; see Figure~\ref{fig special p}). If $n-1 \not\in I_{n-2}^{V}$, then in $W$ the algorithm assigns $p$ to $n-1$ and then proceeds identically to $I_{n-2}^{V}$ for the remainder of its steps; thus $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-1\}$ in this case.

Finally, if $n-2,n-1 \in I_{n-2}^{V}$ then in $W$ the algorithm assigns $q$ to $n-2$ and $p$ to $n-1$ as above, but this is different to what occured in $I_{n-2}^{V}$ so we cannot use the same argument as above. We are now at vertex $n$ and only propagators $p$ and $q$ have been assigned; thus we are proceeding as in the construction of $I_n^{V}$ but without propagator $q$. By Lemma~\ref{vertex cyclic int lem} we know that $q$ was assigned to $n-5$ by $I_n^{V}$, and from the diagram we see that the only way this could occur is if all other propagators in $V$ had already been assigned when we reached vertex $n-5$; thus $q$ was the final propagator to be assigned in $I_n^{V}$. Therefore $I_{n-2}^{W} = (I_{n}^{V} \setminus \{n-5\}) \cup \{n-1, n-2\}$ in this case. This completes all cases for $I_{n-2}^{W}$.

>>>>

Now consider $I_{n-2}^{W}$. If $n-2\not\in I_{n-2}^{V}$ (i.e. $n-2$ supports no propagators in $V$), then $I_{n-2}^W(p) = n-2$ and this assignment of $p$ does not affect the rest of the construction of $I_{n-2}^{V}$, so we obtain $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-2\}$ as above.

On the other hand, if $n-2\in I_{n-2}^{V}$ then we must be in the right hand case of Figure~\ref{fig special p} and $I_{n-2}^V(q) = I_{n-2}^W(q) = n-2$ (since $q$ is always the clockwise-most propagator supported on vertex $n-2$; see Figure~\ref{fig special p}). If $n-1 \not\in I_{n-2}^{V}$, then $I_{n-2}^W(p) = n-1$ and then the algorithm proceeds identically to $I_{n-2}^{V}$ for the remainder of its steps; thus $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-1\}$ in this case.

Finally, if $n-2,n-1 \in I_{n-2}^{V}$ then $I_{n-2}^W(q) = n-2$ and $I_{n-2}^W(p) = n-1$ as above, but this is different to what occured in $I_{n-2}^{V}$ so we cannot use the same argument as above. We are now at vertex $n$ and only propagators $p$ and $q$ have been assigned; thus we are proceeding as in the construction of $I_n^{V}$ but without propagator $q$. By Lemma~\ref{vertex cyclic int lem} we know that $I_n^V(q) = n-5$, and from the diagram we see that the only way this could occur is if all other propagators in $V$ had already been assigned when we reached vertex $n-5$; thus $q$ was the final propagator to be assigned in $I_n^{V}$. Therefore $I_{n-2}^{W} = (I_{n}^{V} \setminus \{n-5\}) \cup \{n-1, n-2\}$ in this case. This completes all cases for $I_{n-2}^{W}$.
